% ──────────────────────────────────────────────
% ACKNOWLEDGEMENT
% ──────────────────────────────────────────────
\begin{center}
{\LARGE \textbf{ACKNOWLEDGEMENT}}
\end{center}
\addcontentsline{toc}{chapter}{Acknowledgement}

\vspace{1cm}

We would like to express our sincere gratitude to all those who contributed to the successful completion of this mini project.

First and foremost, we extend our heartfelt thanks to our project guide, \textbf{Dr. Gilesh M P}, Assistant Professor, Department of Computer Science and Engineering, Government Engineering College, Thrissur, for his invaluable guidance, continuous encouragement, and constructive suggestions throughout the course of this project. His expertise and insights were instrumental in shaping the direction and technical approach of this work.

We are grateful to the \textbf{Head of the Department of Computer Science and Engineering} for providing us with the necessary facilities and support to carry out this project work. We also extend our thanks to the \textbf{Project Coordinator} for the systematic organization and monitoring of the project activities.

We sincerely acknowledge the contributions of all the \textbf{faculty members} of the Department of Computer Science and Engineering, Government Engineering College, Thrissur, whose teachings and mentorship during our coursework provided the foundational knowledge required for this project.

We express our gratitude to \textbf{Dr. K. Raju}, Principal, Government Engineering College, Thrissur, for providing an excellent academic environment and infrastructure.

Finally, we thank our families and friends for their unwavering support, patience, and encouragement throughout this endeavour.

\vspace{1.5cm}

\begin{flushright}
\textbf{Abhinand Ullas P}\\
\textbf{Sagar P}\\
\textbf{Ikramul Haque T K}
\end{flushright}
