\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{References}

\bibitem{supplyco_official}
Kerala State Civil Supplies Corporation Ltd. (SupplyCo). Official Website. Available at: \url{https://supplycokerala.com/}. Accessed: February 2026.

\bibitem{pds_india}
Department of Food and Public Distribution, Ministry of Consumer Affairs, Food and Public Distribution, Government of India. ``Targeted Public Distribution System (TPDS).'' Available at: \url{https://dfpd.gov.in/}. Accessed: January 2026.

\bibitem{digital_india}
Ministry of Electronics and Information Technology, Government of India. ``Digital India Programme.'' Available at: \url{https://www.digitalindia.gov.in/}. Accessed: January 2026.

\bibitem{nipfp_pds}
Balani, S. ``Functioning of the Public Distribution System: An Analytical Report.'' PRS Legislative Research, New Delhi, 2013.

\bibitem{epos_system}
National Informatics Centre (NIC). ``End-to-End Computerisation of TPDS Operations.'' Ministry of Consumer Affairs, Food and Public Distribution, Government of India, 2019.

\bibitem{saxena_mgovern}
Saxena, S. ``Mobile Governance in India: Challenges and Strategies.'' \textit{International Journal of Electronic Government Research}, vol.~16, no.~3, pp.~45--62, 2020.

\bibitem{rajan_supply_chain}
Rajan, R., Nair, S., and Kumar, P. ``Supply Chain Visibility in Public Distribution Systems: A Study of Kerala's Civil Supply Network.'' \textit{Journal of Public Administration and Governance}, vol.~11, no.~2, pp.~112--128, 2021.

\bibitem{onorc_system}
Department of Food and Public Distribution. ``One Nation One Ration Card (ONORC).'' Government of India. Available at: \url{https://www.impds.nic.in/}. Accessed: February 2026.

\bibitem{flutter_docs}
Google LLC. ``Flutter -- Build Apps for Any Screen.'' Flutter Documentation. Available at: \url{https://flutter.dev/docs}. Accessed: January 2026.

\bibitem{supabase_docs}
Supabase Inc. ``Supabase -- The Open Source Firebase Alternative.'' Supabase Documentation. Available at: \url{https://supabase.com/docs}. Accessed: January 2026.

\bibitem{firebase_docs}
Google LLC. ``Firebase Cloud Messaging (FCM).'' Firebase Documentation. Available at: \url{https://firebase.google.com/docs/cloud-messaging}. Accessed: January 2026.

\bibitem{django_docs}
Django Software Foundation. ``Django -- The Web Framework for Perfectionists with Deadlines.'' Django Documentation. Available at: \url{https://docs.djangoproject.com/}. Accessed: January 2026.

\bibitem{postgresql_docs}
The PostgreSQL Global Development Group. ``PostgreSQL: The World's Most Advanced Open Source Relational Database.'' PostgreSQL Documentation. Available at: \url{https://www.postgresql.org/docs/}. Accessed: January 2026.

\bibitem{geolocator_pub}
Baseflow. ``Geolocator -- Flutter Plugin for Location Services.'' Pub.dev. Available at: \url{https://pub.dev/packages/geolocator}. Accessed: February 2026.

\bibitem{kerala_egovern}
Information Kerala Mission (IKM). ``E-Governance Initiatives in Kerala.'' Government of Kerala. Available at: \url{https://ikm.kerala.gov.in/}. Accessed: February 2026.

\end{thebibliography}
